\documentstyle[twoside,fullpage,fancyhead]{article}

\def\toplines{\hrule\hrule\hrule\vspace{2pt}\hrule}
\def\bottomlines{\hrule\vspace{2pt}\hrule\hrule\hrule}
\def\lines{\hrule\hrule}

\pagestyle{fancy}
\lhead[]{UPAC Cinema}
\chead[]{}
\rhead[UPAC Cinema]{}
\lfoot[(c) Vishal Apte -- 1993]{\thepage}
\cfoot[]{}
\rfoot[\thepage]{(c) Vishal Apte -- 1993}

\topmargin=-0.5in

\title{\smallskip\smallskip\toplines\smallskip\smallskip\smallskip
       \Huge A Checklist for Team Leaders
       \smallskip\smallskip\bottomlines\smallskip}
\author{\Large Vishal Apte}
\date{\today}

\begin{document}

\maketitle

\begin{itemize}

\item get a team ready before the Friday of the movie..

\item be at the DCC by 6:00 pm

\item team members for the first show should start arriving by 6:30

\item take 2-3 people and get ice from Russel Sage dining hall -- for 
      concessions..

\item make sure DCC308 is clean {\bf before} the show starts.

\item setup concessions table, with tableclothes. 

\item get tickets/money from fnc.

\item possibly need line security if sellout is close.

\item Ticket prices 
\begin{itemize}
\item  \$2.00 a person w\/ RPI or Sage ID
\item  \$3.00 with no ID (this rule is rarely enforced..)
\item  \$1.00 with a general UPAC card.
\item  FREE with a cinema card.
\item  2 FREE tickets with a chair card.
\end{itemize}

\item all concessions are \$0.50 each
\item individuals working {\bf that night only} will recieve a 50{\%} discount
  on items
  if they choose too. This does not extend to anyone who is not working,
  including chairs.

\item For every showing -- u must have 
\begin{itemize}
\item     2 people selling tickets
\item     2 people selling concessions
\item     2 people ripping tickets
\item     6 people doing security. (which includes cleanup after a showing)\\
       (Security can be covered with fewer, but 6 is ideal.)
\end{itemize}

\item If you ever get to the point where you have nothing to do, ask the
  fnc or the projectionist -- they might need your help.

\end{itemize}

\end{document}
